Secure Composition \\ of Robust and Optimising Compilers \vspace{-1.5em}

### 2024-05-29 csf2/main.tex
fix typo in def of mix
remove last paragraph

\vspace{-1em}
\begin{gather*}
  \begin{align*}
    \ccdce(\irl{\lifz{true}{\expr[_{1}]}{\expr[_{2}]}}) & = \ccdce(\irl{\expr[_{1}]}) &\\
    \ccdce(\irl{\lifz{false}{\expr[_{1}]}{\expr[_{2}]}}) & = \ccdce(\irl{\expr[_{2}]}) &
  \end{align*}
  \\
  % \begin{align*}
  %   \ccdce(\irl{\lbinop{\expr[_{1}]}{\expr[_{2}]}}) & = \lbinop[\irl]{\ccdce(\irl{\expr[_{1}]})}{\ccdce(\irl{\expr[_{2}]})} &
  % \end{align*}
  % \\[0.25cm]
  \begin{align*}
    \cccf(\irl{\expr}) & = \partialeval{\irl{\expr}}{\irl{\hole{\cdot}}} &
  \end{align*}
  \\[0.125cm]
  \begin{align*}
   \partialeval{\irl{x}}{\irl{\substlist}} & = \irl{n} 
   	\qquad\qquad \text{if } \irl{\subst{n}{x}}\in\irl{\substlist} \\
   \partialeval{\irl{x}}{\irl{\substlist}} & = \irl{x} 
   \qquad\qquad \text{if } \irl{\subst{n}{x}}\notin\irl{\substlist} \\
   \partialeval{\irl{\lbinop{n}{m}}}{\irl{\substlist}} & = \irl{k} 
   \qquad\qquad \text{if } \lbinop{\irl{n}}{\irl{m}}=k \\
   %\partialeval{\irl{\lbinop{\expr[_{1}]}{\expr[_{2}]}}}{\irl{\substlist}} & = \lbinop[\irl]{\partialeval{\irl{\expr[_{1}]}}{\irl{\substlist}}}{\partialeval{\irl{\expr[_{2}]}}{\irl{\substlist}}} \\
   \partialeval{\irl{\llet{x}{\valueexpr}{\expr}}}{\irl{\substlist}} & = \partialeval{\irl{\expr}}{\irl{\subst{x}{\valueexpr}\cdot\substlist}} 
  % \\
  % \partialeval{\irl{\lget{x}{\expr}}}{\irl{\substlist}} & = \lget[\irl]{\irl{x}}{\partialeval{\irl{\expr}}{\irl{\substlist}}}
% \end{align*}
\end{align*}
% \\
% \begin{align*}
%   \partialeval{\irl{\llet{x}{\expr[_{1}]}{\expr[_{2}]}}}{\irl{\substlist}} & = \llet[\irl]{\irl{x}}{\partialeval{\irl{\expr[_{1}]}}{\irl{\substlist}}}{\\&\partialeval{\irl{\expr[_{2}]}}{\irl{\substlist}}} \\
%   \partialeval{\irl{\lifz{\expr[_{1}]}{\expr[_{2}]}{\expr[_{3}]}}}{\irl{\substlist}} & = \lifz[\irl]{\partialeval{\irl{\expr[_{1}]}}{\irl{\substlist}}}{\\&\partialeval{\irl{\expr[_{2}]}}{\irl{\substlist}}}{\partialeval{\irl{\expr[_{3}]}}{\irl{\substlist}}} \\
% \end{align*}
\end{gather*}
% \vspace{-3em}

@@

\paragraph*{Speculation Safety Mechanisms}\label{subsec:relw:ssmechs}

With the advent of speculative execution in processors, it is possible to exploit this unusual paradigm leak secrets.
This work has taken inspiration in the sematics of $\Lspec$ and in \Cref{def:trace:ss} from recent formalisations~\cite{guarnieri2018spectector,fabian2022automatic}.
% \MPin{
%  we take SS from exorcising.
%  we do not take SNI from spectector because it is a hypersafety.
%  other work defined similar props. 
% }
% A subsequent line of work~\cite{fabian2022automatic} shows how to modularly define and compose formal semantics that models different speculative execution variants. 
% Recent work~\cite{fabian2024lift} demonstrates how to lift existing secure compilation proofs for security properties related to speculative execution to more powerful properties, i.e., properties defined for languages with a trace model that enables more vulnerabilities, such as combinations of different speculative execution exploits. 
% To this end, they define a lifting framework and demonstrate how a secure compilation proof for a weaker property can be lifted to a stronger one. 
% Contrary to the compositionality framework presented in this paper, these works are only concerned with composing semantics of the respective programming languages, while in this paper, the secure compilers themselves are composed.

@@

\bibliographystyle{IEEEtran}
\bibliography{main}

>>>>

\vspace{-1em}
\begin{gather*}
  \begin{align*}
    \ccdce(\irl{\lifz{true}{\expr[_{1}]}{\expr[_{2}]}}) & = \ccdce(\irl{\expr[_{1}]}) &\\
    \ccdce(\irl{\lifz{false}{\expr[_{1}]}{\expr[_{2}]}}) & = \ccdce(\irl{\expr[_{2}]}) &
  \end{align*}
  \\
  % \begin{align*}
  %   \ccdce(\irl{\lbinop{\expr[_{1}]}{\expr[_{2}]}}) & = \lbinop[\irl]{\ccdce(\irl{\expr[_{1}]})}{\ccdce(\irl{\expr[_{2}]})} &
  % \end{align*}
  % \\[0.25cm]
  \begin{align*}
    \cccf(\irl{\expr}) & = \partialeval{\irl{\expr}}{\irl{\hole{\cdot}}} &
  \end{align*}
  \\[0.125cm]
  \begin{align*}
   \partialeval{\irl{x}}{\irl{\substlist}} & = \irl{n} 
   	\qquad\qquad \text{if } \irl{\subst{n}{x}}\in\irl{\substlist} \\
   \partialeval{\irl{x}}{\irl{\substlist}} & = \irl{x} 
   \qquad\qquad \text{if } \irl{\subst{n}{x}}\notin\irl{\substlist} \\
   \partialeval{\irl{\lbinop{n}{m}}}{\irl{\substlist}} & = \irl{k} 
   \qquad\qquad \text{if } \lbinop{\irl{n}}{\irl{m}}=k \\
   %\partialeval{\irl{\lbinop{\expr[_{1}]}{\expr[_{2}]}}}{\irl{\substlist}} & = \lbinop[\irl]{\partialeval{\irl{\expr[_{1}]}}{\irl{\substlist}}}{\partialeval{\irl{\expr[_{2}]}}{\irl{\substlist}}} \\
   \partialeval{\irl{\llet{x}{n}{\expr}}}{\irl{\substlist}} & = \partialeval{\irl{\expr}}{\irl{\subst{n}{x}\cdot\substlist}} 
  % \\
  % \partialeval{\irl{\lget{x}{\expr}}}{\irl{\substlist}} & = \lget[\irl]{\irl{x}}{\partialeval{\irl{\expr}}{\irl{\substlist}}}
% \end{align*}
\end{align*}
% \\
% \begin{align*}
%   \partialeval{\irl{\llet{x}{\expr[_{1}]}{\expr[_{2}]}}}{\irl{\substlist}} & = \llet[\irl]{\irl{x}}{\partialeval{\irl{\expr[_{1}]}}{\irl{\substlist}}}{\\&\partialeval{\irl{\expr[_{2}]}}{\irl{\substlist}}} \\
%   \partialeval{\irl{\lifz{\expr[_{1}]}{\expr[_{2}]}{\expr[_{3}]}}}{\irl{\substlist}} & = \lifz[\irl]{\partialeval{\irl{\expr[_{1}]}}{\irl{\substlist}}}{\\&\partialeval{\irl{\expr[_{2}]}}{\irl{\substlist}}}{\partialeval{\irl{\expr[_{3}]}}{\irl{\substlist}}} \\
% \end{align*}
\end{gather*}
% \vspace{-3em}

@@

%\paragraph*{Speculation Safety Mechanisms}\label{subsec:relw:ssmechs}

%With the advent of speculative execution in processors, it is possible to exploit this unusual paradigm leak secrets.
%This work has taken inspiration in the sematics of $\Lspec$ and in \Cref{def:trace:ss} from recent formalisations~\cite{guarnieri2018spectector,fabian2022automatic}.
% \MPin{
%  we take SS from exorcising.
%  we do not take SNI from spectector because it is a hypersafety.
%  other work defined similar props. 
% }
% A subsequent line of work~\cite{fabian2022automatic} shows how to modularly define and compose formal semantics that models different speculative execution variants. 
% Recent work~\cite{fabian2024lift} demonstrates how to lift existing secure compilation proofs for security properties related to speculative execution to more powerful properties, i.e., properties defined for languages with a trace model that enables more vulnerabilities, such as combinations of different speculative execution exploits. 
% To this end, they define a lifting framework and demonstrate how a secure compilation proof for a weaker property can be lifted to a stronger one. 
% Contrary to the compositionality framework presented in this paper, these works are only concerned with composing semantics of the respective programming languages, while in this paper, the secure compilers themselves are composed.

@@

\bibliographystyle{IEEEtranS}
\bibliography{main}
